---
title: "hw-lego-Alice-Tang"
output: html_notebook
---

```{r}
view(lego_sales)
```


Exercise 1: What are the three most common first names of purchasers?
```{r}
lego_sales_1 <- lego_sales %>% count(first_name) %>% arrange(desc(n)) %>% head(3)
lego_sales_1
```
Answer: In this sample, the first three common names of purchasers are Jackson, Jacob, and Joseph. 


Exercise 2: What are the three most common themes of Lego sets purchased?
```{r}
lego_sales_2 <- lego_sales %>% count(theme) %>% arrange(desc(n)) %>% head(3)
lego_sales_2
```
Answer: In this sample, the three most common themes of of Lego sets purchased are Star Wars, Nexo Knights, and Gear 


Exercise 3: Among the most common theme of Lego sets purchased, what is the most common subtheme?
```{r}
lego_sales_3 <- lego_sales %>% filter(theme == "Star Wars" | theme == "Nexo Knights" | theme == "Gear", !is.na(subtheme)) %>% count(subtheme) %>% arrange(desc(n)) %>% head(1)
lego_sales_3                                                                                                                                                                                                   
```
Answer: In this sample, among the most common theme of Lego sets purchased, the most common subtheme is Ultimate.


Exercise 4: Create a new variable called age_group and group the ages into the following categories: “18 and under”, “19 - 25”, “26 - 35”, “36 - 50”, “51 and over”.
```{r}
lego_sales_4 <- mutate(lego_sales, age_group = case_when(age <= 18 ~ "18 and under", age <= 25  ~ "19 - 25", age <= 35  ~ "26 - 35", age <= 50  ~ "36 - 50", age <= Inf  ~ "51 and over"))
lego_sales_4
```


Exercise 5: Which age group has purchased the highest number of Lego sets.
```{r}
lego_sales_5 
```
 
