---
title: "hw-lego-Alice-Tang"
output: html_notebook
---

```{r}
view(lego_sales)
```


Exercise 1: What are the three most common first names of purchasers?
```{r}
lego_sales_1 <- lego_sales %>% count(first_name) %>% arrange(desc(n)) %>% head(3)
lego_sales_1
```
Answer: In this sample, the first three common names of purchasers are Jackson, Jacob, and Joseph. 


Exercise 2: What are the three most common themes of Lego sets purchased?
```{r}
lego_sales_2 <- lego_sales %>% count(theme) %>% arrange(desc(n)) %>% head(3)
lego_sales_2
```
Answer: In this sample, the three most common themes of of Lego sets purchased are Star Wars, Nexo Knights, and Gear 


Exercise 3: Among the most common theme of Lego sets purchased, what is the most common subtheme?
```{r}
lego_sales_3 <- lego_sales %>% filter(theme == "Star Wars" | theme == "Nexo Knights" | theme == "Gear", !is.na(subtheme) ) %>% count(subtheme) %>% arrange(desc(n)) %>% head(1)
lego_sales_3                                                                                                                                                                                                   
```
Answer: In this sample, among the most common theme of Lego sets purchased, the most common subtheme is Ultimate.


Exercise 3:


